
Exercise 3.2 From concerts_obo,

Retrieve the 3rd and 5th concert observations and bind the result value with an object name concerts_sampled.

For the second concert, what are its first show’s time and location? Retrieve the information and bind the value with firstShowInfo.

```{r}
concerts_sampled <- concerts_obo[c(3,5)] 
firstShowInfo <- concerts_obo[[2]][["showInfo"]][[1]][c("time","location")]
```


Exercise 3.3 From concerts_obo, due to Covid-19 the 3rd concert’s 1st show time is changed to “2022/01/31 19:30:00” and the location is changed to “Taichung Opera House”, please change the information

```{r}
concerts_obo[[3]][["showInfo"]][[1]][c("time", "location")] <- list("2022/01/31 19:30:00", "Taichung Opera House")
```

Exercise 3.4 How do you add the new born if you use JohnsFamilyCopy3$children[3] <-:
  
  
  Copy
JohnsFamilyCopy3 <- JohnsFamily
JohnsFamilyCopy3$children[3] <-
  
```{r}
JohnsFamilyCopy3 <- JohnsFamily
JohnsFamilyCopy3$children[3] <- list(
  list(
    "Lisa", 
    0
  )
)
```

Exercise 3.5 The 5th concert decides to add one more show which shares the same show information as its first show except the date is 2 days later.

```{r}
concerts_obo[[5]]$showInfo[[2]] <- list()
concerts_obo[[5]]$showInfo[[2]] <- concerts_obo[[5]]$showInfo[[1]]
concerts_obo[[5]]$showInfo[[2]]$time <- "2021/12/20 10:00:00"
concerts_obo[[5]]$showInfo[[2]]$endTime <- "2021/12/21 22:00:00"
```

Exercise 3.6 Due to Covid-19 concerts 2, 5, 7 are cancelled. Remove those three concerts from concerts_obo.

```{r}
concerts_obo <- concerts_obo[-c(2, 5, 7)]
```
