---
title: "Exercise 5.3"
output: html_notebook
---

Exercise 5.3 It is very common that economic model has some equilibrium condition as the intersection of two straight lines, like demand and supply. They can be expressed as:
demand: p_d(q)=a+bq
supply: p_s(q)=c+dq
In equilibrium,
(p*, q*) satisfies p_d(q*)=p_s(q*) and p*=p_d(q*)=p_s(q*).

If you solve for $q*$ and $p*$,
q*=(a-c)/(d-b)
p*=a+bq*.

1. Run the following code and solve for equilibrium and save it in a list with two element names q_star and p_star. Each has its value in corresponding to q* and p* that your program solved.
```{r}
a=1; b=-3; c=0; d=1
# 1
pick5_3_1=list(
  q_star=(a-c)/(d-b), 
  p_star=a+b*q_star
)
pick5_3_1
```

2. Create a function called solve_equilibrium so that the following code would work:
```{r}
# 2
pick5_3_2=list(
  q_star=numeric(1), 
  p_star=numeric(1)
)
solve_equilibrium <- function(){
  pick5_3_2$q_star=(a-c)/(d-b)
  pick5_3_2$p_star=a+b*pick5_3_2$q_star
  pick5_3_2
}

a=1; b=-3; c=0; d=1
equilibrium1 <- solve_equilibrium()
print(equilibrium1)

a=2; b=-3; c=0; d=1
equilibrium2 <- solve_equilibrium()
print(equilibrium2)

a=1; b=-3; c=0; d=1.5
equilibrium3 <- solve_equilibrium()
print(equilibrium3)
```

