---
title: "Exercise 4.19"
output: html_notebook
---

Exercise 4.19 Obtain wdi object from exercise 5 of the Exercise section. The following questions focus only on year 2000 (which means all the following questions implicitly start with the expression, for those from year 2000.)

```{r}
wdi <- list()
wdi$source[[1]] <- "https://databank.worldbank.org/source/world-development-indicators#"
wdi$source[[2]] <- "https://docs.google.com/spreadsheets/d/1XHxjE3DIIdvNL-kbLR_bktxiHxmk23S6lUmn89WEedM/edit?usp=sharing"
wdi$meta <- "https://docs.google.com/spreadsheets/d/1C8b-liC8Gl9Kmkexb5uq1_TUIE3lYOt4PutPlOne80g/edit?usp=sharing"
wdi$data <- googlesheets4::read_sheet(
  wdi$source[[2]]
)
```

1. How many observations are there?

2. The followings are iso2c values that represent a region but not a country. Take a subsample that excludes those region (i.e. a subsample that consists of countries),

```{r}
iso2c_nonCountry <- c('ZH','ZI','1A','S3','B8','V2','Z4','4E','T4','XC','Z7','7E','T7','EU','F1','XE','XD','XF','ZT','XH','XI','XG','V3','ZJ','XJ','T2','XL','XO','XM','XN','ZQ','XQ','T3','XP','XU','XY','OE','S4','S2','V4','V1','S1','8S','T5','ZG','ZF','T6','XT','1W')
```

The following questions focus on the subsample.

3. How many countries are there?

4. Regarding Energy use (kg of oil equivalent per capita). Complete the following summary:

For Energy use (kg of oil equivalent per capita), there are …         observations with … missing values. Excluding missing values, the range of energy use is between … and … kg/per capita of oil equivalent with median usage of … and mean usage of … .

The wdi$data’s feature meanings (other than iso2c, year, and country) can be found at:

```{r}
browseURL(wdi$meta)
```

```{r}
# 1
pick19_1 = wdi$data$year == 2000
sum(as.numeric(pick19_1))
# 2
allIso2c = unique(wdi$data$iso2c)
pick19_2 = !(unique(wdi$data$iso2c) %in% iso2c_nonCountry)
subsample = allIso2c[which(pick19_2)]
subsample
# 3
length(subsample)
# 4
pick19_4_1 = length(wdi$data$EG.USE.PCAP.KG.OE)
pick19_4_2 = sum(as.numeric(is.na(wdi$data$EG.USE.PCAP.KG.OE)))
pick19_4_3 = min(wdi$data$EG.USE.PCAP.KG.OE, na.rm=T)
pick19_4_4 = max(wdi$data$EG.USE.PCAP.KG.OE, na.rm=T)
pick19_4_5 = median(wdi$data$EG.USE.PCAP.KG.OE, na.rm=T)
pick19_4_6 = mean(wdi$data$EG.USE.PCAP.KG.OE, na.rm=T)
paste(
  'For Energy use (kg of oil equivalent per capita), there are', 
  pick19_4_1, 'observations with', 
  pick19_4_2, 'missing values. Excluding missing values, the range of energy use is between', pick19_4_3, 'and', pick19_4_4, 
  'kg/per capita of oil equivalent with median usage of', pick19_4_5, 
  'and mean usage of', pick19_4_6, '.', 
  sep=' '
  )
```

