---
title: "Exercise 4.13"
output: html_notebook
---

```{r}
johnDoe <- list()
johnDoe$source[[1]] <- "https://www.moj.gov.tw/2204/2771/2773/76135/post"
johnDoe$source[[2]] <- "https://docs.google.com/spreadsheets/d/1g2AMop133lCAsmdPhsH3lA-tjiY5fkGIqXqwdknwEVk/edit?usp=sharing"
googlesheets4::read_sheet(
  johnDoe$source[[2]]
) -> johnDoe$data
```

```{r}
johnDoe$data |> View()
```



Exercise 4.13 Regarding johnDoe in exercise 1 of Exercise section,

1.For those whose reported unit (通報機構) is not NA, what are their records? (in other words, construct a reported-unit-not-NA subsample)

2.For those dead bodies reported (通報機構) by “海巡隊” (use =="海巡隊" here. Ignore other similar unit names), what are their death types (死亡方式描述)? How many bodies in each type?

3.For those whose death type (死亡方式描述) is 不詳 or 他殺, what are their discovered counties (發現縣市)? How many such bodies in each counties?
```{r}
# 1
pick13_1 <- !is.na(johnDoe$data$通報機關名稱)
johnDoe$data$編號[which(pick13_1)]
johnDoe$data[pick13_1, ] -> subsample
View(subsample)
# 2
pick13_2 <- johnDoe$data$通報機關名稱 == "海巡隊"
johnDoe$data$死亡方式描述 [which(pick13_2)]
table(johnDoe$data$死亡方式描述 [which(pick13_2)])
# 3
pick13_3 <- johnDoe$data$死亡方式描述 == "不詳" | johnDoe$data$死亡方式描述 == "他殺"
johnDoe$data$發現縣市 [which(pick13_3)]
table(johnDoe$data$發現縣市 [which(pick13_3)])
```