---
title: "Exercise 5.2"
output: html_notebook
---

```{r}
drug <- list()
drug$source[[1]] <- 
  "https://docs.google.com/spreadsheets/d/17ID43N3zeXqCvbUrc_MbpgE6dH7BjLm8BHv8DUcpZZ4/edit?usp=sharing"
drug$data <- 
  googlesheets4::read_sheet(
    drug$source[[1]]
  )
```

Exercise 5.2 Regarding the drug data from Exercise 4.8.

1. For each kind of drug (毒品品項), what was the average amount of drug (the mean of 數量（淨重）_克) found?

2. Add a column date to the data frame which is a date class created from the column 發生日期

For the following question, we only consider those 毒品品項 that contains the words “安非他命”.

3. For each year, what was the total amount found? (Apply lubridate::year() to date column will get you year)

```{r}
# 1
pick5_2_1 <- list()
for(.x in c(2:length(drug$data$weight_g))){
  pick5_2_1[[.x-1]] <- drug$data$weight_g[[.x]]
}
mean(as.numeric(pick5_2_1))
# 2
pick5_2_2 <- vector("character", length=length(drug$data$weight_g))
drug$data[,c("no", "type", "oc_dt", "date", "oc_addr", "oc_p1", "oc_p2", "oc_p3", "proc_no", "kind", "weight_g")]
for(.x in c(2:length(drug$data$date))){
  pick5_2_2[[.x]] <- as.numeric(drug$data$oc_dt[[.x]])+19110000
}
drug$data$date <- lubridate::ymd(pick5_2_2)
# 3
pick5_2_3 <-  vector("character", length=length(drug$data$date))
for(.x in c(2:length(drug$data$date))){
  pick5_2_3[[.x]] <- lubridate::year(drug$data$date[[.x]])
}
pick5_2_3[[1]] <- NA
table(pick5_2_3)
```