---
title: "Exercise 4.8"
output: html_notebook
---

Exercise 4.8 A school adopt letter grade system from C to A+ as follows:
```{r}
letter_grades <- c("C", "B-", "B", "B+", "A-", "A", "A+")
```

However, when there is need to calulate GPA, they convert each letter grade to each value in the following numeric_grades vector:
```{r}
numeric_grades <- c(2, 2.5, 3, 3.5, 4, 4.5, 5)
```

A student with the following letter grades need to convert them to numeric_grades:
```{r}
studentGrades <- c('B','A','A+','B+','A-','B','B-','B','A+','B+','C','B-','B-','B','C','C','B+','B','B+','B')
```
He asked you for help. You layout the following programming plan:
```{r}
studentLetterGrades <- {
  # Task map c("C", "B-", "B", "B+", "A-", "A", "A+") to c(2, 2.5, 3, 3.5, 4, 4.5, 5)
  
  # step1: for each grade in studentGrades find its position in c("C", "B-", "B", "B+", "A-", "A", "A+") so if studentGrades = c("C","A-"), step1 = c(1, 5) since c("C", "B-", "B", "B+", "A-", "A", "A+")[c(1, 5)] will give him "C", "A-"
  step1 <- as.numeric(
    factor(
      studentGrades, 
      levels=letter_grades
      )
    )
  # step2: Use step1 result as position indices to retrieve from c(2, 2.5, 3, 3.5, 4, 4.5, 5). From previous example, step1=c(1, 5), then  c(2, 2.5, 3, 3.5, 4, 4.5, 5)[step1] will give him c(2, 4)
  step2 <- factor(
    step1 * 0.5 + 1.5,
    levels=numeric_grades
  )
}
```
Complete the programming block.


