---
title: "Exercise 4.3"
output: html_notebook
---
Exercise 4.3 Data frame parsing exercise:

1.Declare a list named dfExercise.

```{r}
dfExercise <- list()
```

The following feature-by-feature data set (dataSet1) collects name and age of three persons:

```{r}
dataSet1 <- list(
  name=c("John", "Mary", "Ben"),
  age=c(33, 45, NA)
)
dfExercise$data1 <-
  data.frame(
    dataSet1
  )
dfExercise
```
2.Please parse the data set into a data frame class and add the parsed data frame to dfExercise$data1.

3.We want to add another feature to dataSet1 called children. We want:

```{r}
dataSet1$children <- list(
  list(list()), 
  list(list(),list()), 
  list(list())
)
dataSet1$children[[1]][[1]] <- list(name="Jane", age=2)# shows the first person's 1st child: name is Jane, age is 2
dataSet1$children[[2]][[1]] <- list(name="Bill", age=3)# shows the second person's 1st child: name is Bill, age =3
dataSet1$children[[2]][[2]] <- list(name="Ken", age=0)# the second pseron's 2nd child: name is Ken, age=0
dataSet1$children[[3]][[1]] <- list(name="William", age=10)# the 3rd person's 1st child: name is William, age =10
dfExercise$data2 <-
  data.frame(
    dataSet1$children
  )
```

4.After adding another feature to dataSet1, parse it to a data frame and save the value at dfExercise$data2.

