---
title: "week10"
output: html_notebook
---

# 4.2.3 Date/Time
```{r}
install.packages("lubridate")
```

```{r}
lubridate::ymd(c("2021/10/30", "2021-10-30", "2021 October 30", "2021 Oct. 30"))
lubridate::ydm(c("2021/30/10", "2021-30-10", "2021 30 October", "2021 30 Oct."))
lubridate::mdy(c("10/30/2021", "10-30-2021", "October 30, 2021", "Oct. 30, 2021"))
lubridate::dmy(c("30/10/2021", "30-10-2021", "30 October, 2021", "30 Oct., 2021"))
```

```{r}
dayInfo <- list()
dayInfo <- c("2021/10/30", "2021-10-30", "2021 October 30", "2021 Oct. 30")
class(dayInfo$ymd)
lubridate::ymd(dayInfo$ymd) -> dayInfo$ymd_parsed
```

```{r}
commonClasses <- list()

# save three different atomic vectors
commonClasses$character <- c("John", "Mary", "Bill")
commonClasses$numeraic <- c(2, 3, 4, 7)
commonClasses$logical <- c(TRUE, T, F, FALSE)
```

```{r}
# A parsed date data has Date class.
commonClasses$date <- lubridate::dmy(c("30/10/2021", "30-10-2021", "30 October, 2021", "30 Oct., 2021"))
class(commonClasses$date)
```

"2021/10/30 13:22:52"

* day style: ymd
* time style: hms

```{r}
lubridate::ymd_hms(
  "2021/10/30 13:22:52", 
  tz="Asia/Taipei"
) -> dateTime_taipei

dateTime_taipei
```

```{r}
dateTime_taipei <- 
  lubridate::ymd_hms(
    c("2021/10/30 13:22:52", "2021-10-31 1:22:52PM"),
    tz = "Asia/Taipei")
dateTime_taipei
```

```{r}
dateTime_london <- 
  lubridate::mdy_hm(
    c("October 30, 2021, 23:10", "Oct. 30, 2021 11:10PM"),
    tz="Europe/London")
dateTime_london
```

```{r}
c(
  dateTime_taipei, # name call on dateTime_taipei
  dateTime_london # name call on dateTime_london
) # can form an atomic vector since they share the same class.
```

```{r}
commonClasses$date_time <- c(
  dateTime_taipei,
  dateTime_london
)
class(commonClasses$date_time)
```

```{r}
dateTime_london # name call on dateTime_london
dateTime_london_atTaipei <-
  lubridate::with_tz(
    dateTime_london, # must be a date/time class
    tz="Asia/Taipei"
  )
dateTime_london
dateTime_london_atTaipei
```

```{r}
lubridate::with_tz(
  c("October 30, 2021, 23:10", "Oct. 30, 2021 1:10AM"),
  tz="Asia/Taipei"
)

lubridate::with_tz(
  c("John", "Mary"),
  tz="Asia/Taipei"
)
```


# 4.2.4 Date frame
```{r}
survey_fbf <-
  list(
    age=c(54, 32, 28, 20), # age
    gender=c("male", "female", "female", "male"), # gender
    residence=c("north", "south", "east", "east"), # residence
    income=c(100, 25, NA, 77) # income
  )
```

```{r}
data.frame(
  data_list # atomic feature vectors and named with same length
)
```

```{r}
survey_df <-
  data.frame(
    survey_fbf # name call on survey_fbf
  )
```

```{r}
class(survey_fbf)
class(survey_df)
```

```{r}
survey_df <-
  data.frame(
    age=c(54, 32, 28, 20), # age
    gender=c("male", "female", "female", "male"), # gender
    residence=c("north", "south", "east", "east"), # residence
    income=c(100, 25, NA, 77) # income
  )
```

```{r}
commonClasses <- list()
commonClasses$data_frame <- survey_df
```

***
feature vectors not all atomic vectors--some are list
```{r}
survey_fbf2 <-
  list(
    age=list(54, 32, 28, 20), # age
    gender=list("male", "female", "female", "male"), # gender
    residence=list("north", "south", "east", "east"), # residence
    income=list(100, 25, NA, 77) # income
  )
```

```{r}
data.frame(survey_fbf2) #the same as
data.frame(
  list(
    age=list(54, 32, 28, 20), # age
    gender=list("male", "female", "female", "male"), # gender
    residence=list("north", "south", "east", "east"), # residence
    income=list(100, 25, NA, 77) # income
  )
)
```

```{r}
df_survey_fbf2 <- list2DF(survey_fbf2)

df_survey_fbf2
```

data frame is an extended class from list. It inherits all the features of list.

```{r}
survey_fbf$age
df_survey_fbf <- data.frame(survey_fbf)
df_survey_fbf$age
```

- inheritance feature from Object-Oridnted Programming (OOP)

```{r}
# list
survey_fbf2$age
# data frame
df_survey_fbf2$age
```

```{r}
df_survey_fbf
df_survey_fbf2
```

not only inheris methods of list (what list can do), but also has more methods (but also can do more)

```{r}
[.row, .col] # is an extension from [] extraction
```

```{r}
commonClasses$data_frame
commonClasses$data_frame[2, "age"]
commonClasses$data_frame[2, 1]
commonClasses$data_frame[c(1,4), c("income","age")]
commonClasses$data_frame[c(1,4), c(4, 1)]
```

*[], [.ral, .col] will return value with a structure as the source.

```{r}
# Remove
commonClasses$data_frame
commonClasses$data_frame[, -c(2)]
# Replace
commonClasses$data_frame
commonClasses$data_frame[2, c( "age","income")] <- data.frame(
  age=c(31), 
  income=c(22)
)
## == commonClasses$data_frame[2, c( "age","income")] <- data.frame(
##      31, 
##      22
##    )
commonClasses$data_frame[c(1,2), c("age", "income")]
commonClasses$data_frame[c(1,2), c("age", "income")] <- data.frame(
  age=c(10, 15),
  income=c(10, 15)
)
commonClasses$data_frame[c(1,2), c("age", "income")]
# Add
commonClasses$data_frame[, "isStudent"] <- data.frame(isStudent=c(T, T, F, T))
## == commonClasses$data_frame[, "isStudent"] <- data.frame(c(T, T, F, T))
## == commonClasses$data_frame[, "isStudent"] <- c(T, T, F, T)
```

```{r}
# a list
survey_fbf[2, c(1, 3)]
# a data frame
survey_df[2, c(1, 3)]
```

# 4.2.5 Matrix
```{r}
commonClasses$matrix <- matrix(
  c(2, 11, -1, 3, 4, -5), 
  nrow=2, 
  byrow = T # default is by column
)
commonClasses$matrix
class(commonClasses$matrix)
```

```{r}
# non atomic matrix
matrix_nonAtomic <- matrix(
  list(
    32, "John", 
    33, "Jane", 
    34, "Ben"
    ), nrow=2
)
matrix_nonAtomic
```
